hbm_paper_results

### 2024-05-23 paper_prop_results.Rmd
cleaning and updating

source("./cubic_scripts/R_scripts/stats_tests.R")
#aseg_cerebrum <- readRDS(file="/Users/megardn/Desktop/BGD_Repos/ggseg_atlas/aseg_cerebrum_atlas.RDS")
```

@@

```{r}
dataset_names <- c('ukb-CN-simsites' = "Raw Data",  cf = "ComBat w/o cov", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
n_prop_list <- c("0M:10F", "1M:9F", "2M:8F", "3M:7F", "4M:6F", "5M:5F", "6M:4F", "7M:3F", "8M:2F", "9M:1F", "10M:0F")
```

@@

```{r, eval=FALSE}
ratio.df %>%
  ggplot() +
  geom_violin(aes(y=diff_GMV, x= sex, fill=sim.site)) +
  facet_grid(dataset~prop, scales="free_y")

@@

Read in predicted centiles & z scores FROM RAW DATA ONLY (to save memory)
```{r, eval=FALSE}
pred.csvs <- list.files(path = data_path, pattern = "raw_predictions.csv", full.names = TRUE)

@@

```{r, eval=FALSE}
percent_f <- setNames(paste0(seq(from=100, to=0, by=-10), "% F"), unique(ratio.df$prop))

ratio.df %>%
  mutate(sex_site = paste(sex, sim.site, sep=".")) %>%
  dplyr::filter(dataset=="cf") %>%
ggplot() +
  geom_bar(aes(x=prop, fill=sex_site)) +
  scale_x_discrete(labels=percent_f) +
  scale_fill_manual(values=c(Female.Balanced = "#FCC3BF", Male.Balanced = "#ADFDFF", Female.Imbalanced ="#F8766D", Male.Imbalanced="#00BFC4")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_hline(yintercept = (18800/2), linetype="dashed")+
  theme_linedraw()
```

@@

add significance testing
```{r}
cent.t.test.df_global <- fread(paste0(data_path, "/full_featurewise_cent_t_tests_global.csv"))

cent.t.test.df_global_filt <- cent.t.test.df_global %>%
  dplyr::filter(comp %in% c("cf.gamlss_cf.gam", "cf.lm_cf.gam", "cf.lm_cf.gamlss"))

cent.t.test.df_global_filt %>%
  dplyr::filter(sig_fdr == FALSE)
```

@@

# mean_comp_tbl <- ggpubr::compare_means(abs.diff ~ dataset, data=prop.global_abs.diffs, group.by = c("pheno", "prop")) 
# unique(mean_comp_tbl$group1)
# unique(mean_comp_tbl$group2)
mean_comp_tbl_calc <- prop.global_abs.diffs %>%
  group_by(pheno, prop) %>%
  pairwise_wilcox_test(abs.diff ~ dataset, comparisons=list(c("cf.lm", "cf.gam"), c("cf.gam", "cf.gamlss"), c("cf.lm", "cf.gamlss")),
                       p.adjust.method = "fdr")

mean_comp_tbl <- mean_comp_tbl_calc %>%
  mutate(comp = factor(paste(group1, group2, sep="_"), ordered=TRUE, levels=c("cf.gamlss_cf.lm", "cf.gam_cf.lm", "cf.gam_cf.gamlss"))) %>%
  arrange(prop, comp) %>%
  add_xy_position(x="prop", fun="max", comparisons=list(c("cf.lm", "cf.gam"), c("cf.gam", "cf.gamlss"), c("cf.lm", "cf.gamlss"))) %>%
  add_significance("p.adj")

#check ns results
mean_comp_tbl %>%
  dplyr::filter(p.adj.signif == "ns")

#get max w/in each pheno, prop & dataset
max_abs.errs <- prop.global_abs.diffs %>%
  group_by(pheno, prop, dataset) %>%
  summarize(max_err = max(abs.diff)) %>%
  ungroup() %>%
  pivot_wider(id_cols=c(pheno, prop), names_from=dataset, values_from=max_err, names_prefix="max_")

@@

mean_comp_tbl3 <- mean_comp_tbl2 %>%
  mutate(p.adj.signif = ifelse(p.adj.signif == "ns", "ns", "*"),
         xmax=case_when(group1=="cf.gamlss" | group2== "cf.gamlss" ~ (x+.266667),
                        TRUE ~  x),
         xmin=case_when(group2=="cf.lm" ~ (x-.266667),
                        TRUE ~  x),
         y.position=case_when(comp == "cf.gamlss_cf.lm" ~ max_cf.lm + 3.3,
                              comp == "cf.gam_cf.lm" ~ max_cf.lm + 2,
                              TRUE ~ max_cf.gam + 1.8))
mean_comp_tbl3[(mean_comp_tbl3$pheno=="WMV" & mean_comp_tbl3$group1=="cf.gam"), "p.adj.signif"] <- "*" #Overwrite result that doesnt match
mean_comp_tbl3 %>%
  dplyr::filter(p.adj.signif == "ns")
```
results match! just gotta proceed as is

@@

prop.global_cent_errs_plot <- prop.global_abs.diffs %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("WMV", "GMV", "sGMV", "Ventricles"), ordered = TRUE)) %>%
  ggplot() +
  geom_violin(aes(x=prop, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Absolute Centile Error", x = "% Females in Imbalanced Site") +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "bottom") +
  scale_x_discrete(labels=percent_f) +
  stat_pvalue_manual(mean_comp_tbl3, label = "p.adj.signif", label.size = 2, tip.length = 0) +
  # ggsignif::geom_signif(data=mean_comp_tbl2) +
  facet_wrap(~ pheno)
  # ggtitle("Magnitude errors in centile scores of global features across \nComBat pipelines")
prop.global_cent_errs_plot
#ggsave("figs/global_centile_errors.jpeg", global_cent_errs_plot)
```

Also visualize by sex
```{r, eval=FALSE}
prop.global_cent_errs_plot_bysex <- prop.global_abs.diffs %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("WMV", "GMV", "sGMV", "Ventricles"), ordered = TRUE),
         abs.diff = abs.diff*100) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=prop, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Magnitude Centile Error", x = "% Females in Imbalanced Site") +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "bottom") +
  scale_x_discrete(labels=percent_f) +
  facet_grid(sex ~ pheno) +
  ggtitle("Magnitude errors in centile scores of global features across \nComBat pipelines")
# prop.global_cent_errs_plot_bysex
```

@@

```{r}
cent.feat.sex.test.df <- cent.feat.sex.test.df %>%
  mutate(pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)))

cent.feat.sex.test.df %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff*100)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= pheno_cat, color=pheno_cat), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(prop~dataset, scales="free")

t.test.cent.sex.diff <- cent.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  group_by(dataset, pheno_cat, prop) %>%
  summarise(t.test.p = tidy(t.test(median_sex_diff, mu=0))$p.value,
            max_val = max(median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = (3*4*11)), #not testing global vols, too few data points
                  sig_fdr_tf = case_when(p.val_fdr < 0.05 ~ TRUE,
                                      p.val_fdr >= 0.05 ~ FALSE),
         sig_fdr = case_when(
           # p.val_fdr < 0.001 ~ "***",
           #                     p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
           #                     p.val_fdr >= 0.01 & 
                               p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         y_pos = ifelse(max_val < 0, ((max_val*100)*0.5), (max_val*100)+0.8))

cortical_cent_sex_diff.plt <- cent.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume" & dataset != "cf") %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
    facet_grid(dataset~pheno_cat, labeller=labeller(dataset=dataset_names)) + 
  geom_text(aes(label = sig_fdr, y = y_pos),
              data = t.test.cent.sex.diff[which(t.test.cent.sex.diff$dataset != "cf"),]) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)

#just global volumes
cent.feat.sex.test.df %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  dplyr::filter(pheno_cat == "Global Volume") %>%
  ggplot() +
  geom_dotplot(aes(x=prop, y=median_sex_diff, color=dataset, fill=dataset), binaxis = "y", stackdir="center") +
    facet_grid(pheno_cat~dataset, scales="free_y", labeller=labeller(dataset=dataset_names)) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  scale_fill_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)

#zoom in on combat-GAM vs combat-LS
cent.feat.sex.test.df %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  #mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              #TRUE ~ median_sex_diff*100)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= dataset, color=dataset), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_wrap(~prop, labeller = as_labeller(percent_f), scales="free") +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

@@

```{r, eval=FALSE}
#stats test
global_sex_diffs <- cent.feat.sex.test.df %>%
  dplyr::filter(pheno %in% vol_list_global & dataset %in% c("cf.gam", "cf.gamlss")) %>%
  mutate(pheno_prop = paste(pheno, prop, sep="&"))

global_sex_errs.df <- ratio.df %>%
  dplyr::select(participant, sex, age_days, sim.site, prop, dataset, paste0("diff_", vol_list_global)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff")

wilcox_tbl <- global_sex_errs.df %>%
  mutate(pheno_prop = paste(pheno, prop, sep="&"),
         pheno = factor(pheno, levels = c("GMV", "sGMV", "Ventricles", "WMV"), ordered = TRUE),
         diff=diff*100) %>%
  arrange(pheno, prop) %>%
  group_by(dataset, pheno, prop) %>%
  wilcox_test(diff ~ sex) %>%
  add_xy_position(x="prop", fun="max")

stat_merge <- full_join(wilcox_tbl, global_sex_diffs)
stat_merge2 <- stat_merge %>%
  add_significance("p.val_fdr") %>% #use actual cubic test (nonparametric, full fdr correction) for significance labels
  mutate(p.val_fdr.signif = ifelse(p.val_fdr.signif == "ns", "", "*")) 
table(stat_merge2$p.val_fdr.signif, stat_merge2$sig_fdr)
```

```{r, eval=FALSE}
sex_err_ratio.plt <- ratio.df %>%
  dplyr::select(participant, sex, age_days, sim.site, prop, dataset, paste0("diff_", vol_list_global)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("GMV", "sGMV", "Ventricles", "WMV"), ordered = TRUE),
         diff = diff*100,
         pheno_prop = paste(pheno, prop, sep="&")) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=prop, y=diff, fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  # scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  # scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Centile Error", x = "% Females in Imbalanced Site") +
  stat_pvalue_manual(stat_merge2, label = "p.val_fdr.signif", label.size = 3, tip.length = 0, hide.ns = TRUE, remove.bracket = TRUE) +
  scale_x_discrete(labels=percent_f) +
  # facet_wrap(~dataset, labeller=labeller(dataset=dataset_names), nrow=2, strip.position = "right") +
  # guides(x = ggh4x::guide_axis_nested(delim = "&", inv=TRUE)) +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "bottom") +
  labs(fill="Sex", color="Sex")+
  facet_grid(dataset ~ pheno, labeller=labeller(dataset=dataset_names), scales="free_x")
  # ggtitle("Errors in centile scores of global features in ComBat-GAM and ComBatLS")
sex_err_ratio.plt
```

@@

#compare with full dataset
cortical_cent_sex_diff.plt
```
similar overall pattern

@@

Plot errors for global phenotypes
```{r}
percent_f <- setNames(paste0(seq(from=100, to=0, by=-10), "% F"), unique(ratio.df$prop))

>>>>

source("./cubic_scripts/R_scripts/stats_tests.R")
```

@@

```{r}
dataset_names <- c('raw' = "Raw Data",  cf = "ComBat w/o cov", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
n_prop_list <- c("0M:10F", "1M:9F", "2M:8F", "3M:7F", "4M:6F", "5M:5F", "6M:4F", "7M:3F", "8M:2F", "9M:1F", "10M:0F")
```

@@

```{r}
ratio.df %>%
  ggplot() +
  geom_violin(aes(y=diff_GMV, x= sex, fill=sim.site)) +
  facet_grid(dataset~prop, scales="free_y")

@@

Read in predicted centiles & z scores FROM RAW DATA ONLY (to save memory)
```{r}
pred.csvs <- list.files(path = data_path, pattern = "raw_predictions.csv", full.names = TRUE)

@@

@@

add significance testing
```{r}
cent.t.test.list <- readRDS(paste0(data_path, "/full_featurewise_cent_t_tests_all_out.RDS"))

cent.t.test.list_global <- lapply(cent.t.test.list, function(x) filter(x, pheno %in% vol_list_global))
cent.t.test_global <- bind_rows(cent.t.test.list_global, .id = "prop") %>%
  dplyr::mutate(prop = case_when(prop == "0M:10F" ~ "prop-01", 
                                 prop == "1M:9F" ~ "prop-02", 
                                 prop == "2M:8F" ~ "prop-03", 
                                 prop == "3M:7F" ~ "prop-04", 
                                 prop == "4M:6F" ~ "prop-05", 
                                 prop == "5M:5F" ~ "prop-06", 
                                 prop == "6M:4F" ~ "prop-07", 
                                 prop == "7M:3F" ~ "prop-08", 
                                 prop == "8M:2F" ~ "prop-09", 
                                 prop == "9M:1F" ~ "prop-10", 
                                 prop == "10M:0F" ~ "prop-11",
                                 TRUE ~ NA_character_))

cent.t.test.df_global_filt <- cent.t.test_global %>%
  dplyr::filter(comp %in% c("cf.gamlss_cf.gam", "cf.lm_cf.gam", "cf.lm_cf.gamlss")) %>%
  dplyr::mutate(comp = factor(comp, ordered=TRUE, levels=c("cf.lm_cf.gam", "cf.lm_cf.gamlss", "cf.gamlss_cf.gam")))
```

@@

#wilcox test for visualizing significance
mean_comp_tbl_calc <- prop.global_abs.diffs %>%
  group_by(pheno, prop) %>%
  pairwise_wilcox_test(abs.diff ~ dataset, comparisons=list(c("cf.lm", "cf.gam"), c("cf.gam", "cf.gamlss"), c("cf.lm", "cf.gamlss")),
                       p.adjust.method = "fdr") 
```

```{r}
mean_comp_tbl <- mean_comp_tbl_calc %>%
  mutate(comp = factor(paste(group2, group1, sep="_"), ordered=TRUE, levels=c("cf.lm_cf.gam", "cf.lm_cf.gamlss", "cf.gamlss_cf.gam"))) %>%
  arrange(prop, comp) %>%
  add_xy_position(x="prop", fun="max", comparisons=list(c("cf.lm", "cf.gam"), c("cf.gam", "cf.gamlss"), c("cf.lm", "cf.gamlss"))) %>%
  add_significance("p.adj")

#get max w/in each pheno, prop & dataset for placement
max_abs.errs <- prop.global_abs.diffs %>%
  group_by(pheno, prop, dataset) %>%
  summarize(max_err = max(abs.diff)) %>%
  ungroup() %>%
  pivot_wider(id_cols=c(pheno, prop), names_from=dataset, values_from=max_err, names_prefix="max_")

@@

#just use significance from actual stats tests

stats_centile_for_plot <- inner_join(mean_comp_tbl2, cent.t.test.df_global_filt)
#kinda hacky way of fixing positions
stats_centile_for_plot.corrected <- stats_centile_for_plot %>%
  mutate(p.adj.signif = ifelse(sig_fdr == "FALSE", "ns", "*"),
         xmax=case_when(group1=="cf.gamlss" | group2== "cf.gamlss" ~ (x+.266667),
                        TRUE ~  x),
         xmin=case_when(group2=="cf.lm" ~ (x-.266667),
                        TRUE ~  x),
         y.position=case_when(comp == "cf.lm_cf.gamlss" ~ max_cf.lm + 1,
                              comp == "cf.lm_cf.gam" ~ max_cf.lm + .5,
                              TRUE ~ max_cf.gam + 0.4))

cent.t.test.df_global_filt %>%
  dplyr::select(prop, comp, pheno, sig_fdr) %>%
  dplyr::filter(sig_fdr == FALSE)
```

@@

prop.global_cent_errs_plot <- prop.global_abs.diffs %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("WMV", "GMV", "sGMV", "Ventricles"), ordered = TRUE)) %>%
  ggplot() +
  geom_violin(aes(x=prop, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Absolute Centile Error", x = "% Females in Imbalanced Site") +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "bottom") +
  scale_x_discrete(labels=percent_f) +
  stat_pvalue_manual(stats_centile_for_plot.corrected, label = "p.adj.signif", label.size = 2, tip.length = 0) +
  # ggsignif::geom_signif(data=mean_comp_tbl2) +
  facet_wrap(~ pheno)
  # ggtitle("Magnitude errors in centile scores of global features across \nComBat pipelines")
prop.global_cent_errs_plot
#ggsave("figs/global_centile_errors.jpeg", global_cent_errs_plot)
```

Visualize by sex

```{r}
prop.global_abs.diffs %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("WMV", "GMV", "sGMV", "Ventricles"), ordered = TRUE)) %>%
  ggplot() +
  geom_violin(aes(x=prop, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Absolute Centile Error", x = "% Females in Imbalanced Site") +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "bottom") +
  scale_x_discrete(labels=percent_f) +
  facet_grid(sex ~ pheno)
```

@@

@@

add significance testing

```{r}
cent.feat.test_global <- cent.feat.sex.test.df %>%
  dplyr::filter(pheno_cat == "Global Volume" & (dataset == "cf.gam" | dataset =="cf.gamlss"))

#wilcox test for visualizing significance
cent.sex_comp_tbl_calc <- ratio.df %>%
  dplyr::select(participant, sex, prop, dataset, paste0("diff_", vol_list_global)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  group_by(dataset, pheno, prop) %>%
  wilcox_test(diff ~ sex)

cent.feat.test_global %>%
  dplyr::filter(pheno=="WMV") %>%
  dplyr::select(dataset, pheno, prop, sig_fdr)
```

```{r}
cent.sex_comp_tbl <- cent.sex_comp_tbl_calc %>%
  arrange(prop) %>%
  add_xy_position(x="prop", fun="max") %>%
  add_significance("p")

#get max w/in each pheno, prop & dataset for placement
max_errs <- ratio.df %>%
  dplyr::select(participant, sex, prop, dataset, paste0("diff_", vol_list_global)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  group_by(pheno, prop, dataset) %>%
  summarize(max_diff = max(diff)) %>%
  ungroup() %>%
  pivot_wider(id_cols=c(pheno, prop), names_from=dataset, values_from=max_diff, names_prefix="max_")

cent.sex_comp_tbl2 <- full_join(cent.sex_comp_tbl, max_errs)

#just use significance from actual stats tests

stats_sex.centile_for_plot <- inner_join(cent.sex_comp_tbl2, cent.feat.test_global)
#kinda hacky way of fixing positions
stats_sex.centile_for_plot.corrected <- stats_sex.centile_for_plot %>%
  mutate(p.adj.signif = ifelse(sig_fdr == "FALSE", "ns", "*"),
         y.position=case_when(dataset=="cf.gam" ~ max_cf.gam*100+0.5,
                           dataset=="cf.gamlss" ~ max_cf.gamlss*100+0.5,
                           TRUE ~ NA))

sex_err_ratio.plt <- ratio.df %>%
  dplyr::select(participant, sex, age_days, sim.site, prop, dataset, paste0("diff_", vol_list_global)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("GMV", "sGMV", "Ventricles", "WMV"), ordered = TRUE),
         diff = diff*100,
         pheno_prop = paste(pheno, prop, sep="&")) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=prop, y=diff, fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  labs(y="Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f) +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "bottom") +
  labs(fill="Sex", color="Sex")+
  stat_pvalue_manual(stats_sex.centile_for_plot.corrected, label = "p.adj.signif", label.size = 2, tip.length = 0) +
  facet_grid(dataset ~ pheno, labeller=labeller(dataset=dataset_names), scales="free_x")
sex_err_ratio.plt
```

```{r}
t.test.cent.sex.diff <- cent.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  group_by(dataset, pheno_cat, prop) %>%
  summarise(t.test.p = tidy(t.test(median_sex_diff, mu=0))$p.value,
            max_val = max(median_sex_diff)*100) %>% #test median of each distribution against 0, then scale to centiles
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = (3*4*11)), #not testing global vols, too few data points
                  sig_fdr_tf = case_when(p.val_fdr < 0.05 ~ TRUE,
                                      p.val_fdr >= 0.05 ~ FALSE),
         sig_fdr = case_when(p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         y_pos = max_val + 0.1)

cortical_cent_sex_diff.plt <- cent.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume" & dataset != "cf") %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
    facet_grid(dataset~pheno_cat, labeller=labeller(dataset=dataset_names), scales="free_y") + 
  geom_text(aes(label = sig_fdr, y = y_pos),
              data = t.test.cent.sex.diff[which(t.test.cent.sex.diff$dataset != "cf"),]) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)

cortical_cent_sex_diff.plt
```

COME BACK TO THIS AFTER LOOKING AT REPLICATION PLOTS

@@

#compare with full dataset
cortical_cent_sex_diff.plt
```

similar overall pattern

@@

add significance testing
```{r}
z.t.test.list <- readRDS(paste0(data_path, "/full_featurewise_z_t_tests_all_out.RDS"))

z.t.test.list_global <- lapply(z.t.test.list, function(x) filter(x, pheno %in% paste0(vol_list_global, ".z")))
z.t.test_global <- bind_rows(z.t.test.list_global, .id = "prop") %>%
  dplyr::mutate(prop = case_when(prop == "0M:10F" ~ "prop-01", 
                                 prop == "1M:9F" ~ "prop-02", 
                                 prop == "2M:8F" ~ "prop-03", 
                                 prop == "3M:7F" ~ "prop-04", 
                                 prop == "4M:6F" ~ "prop-05", 
                                 prop == "5M:5F" ~ "prop-06", 
                                 prop == "6M:4F" ~ "prop-07", 
                                 prop == "7M:3F" ~ "prop-08", 
                                 prop == "8M:2F" ~ "prop-09", 
                                 prop == "9M:1F" ~ "prop-10", 
                                 prop == "10M:0F" ~ "prop-11",
                                 TRUE ~ NA_character_))

z.t.test.df_global_filt <- z.t.test_global %>%
  dplyr::filter(comp %in% c("cf.gamlss_cf.gam", "cf.lm_cf.gam", "cf.lm_cf.gamlss")) %>%
  dplyr::mutate(comp = factor(comp, ordered=TRUE, levels=c("cf.lm_cf.gam", "cf.lm_cf.gamlss", "cf.gamlss_cf.gam")))
```

```{r}
z.prop.global_abs.diffs <- ratio.df %>%
  dplyr::select(participant, sex, age_days, sim.site, prop, dataset, paste0("abs.diff_", vol_list_global, ".z")) %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  pivot_longer(cols=starts_with("abs.diff_"), names_to="pheno", names_prefix="abs.diff_", values_to = "abs.diff") %>%
  arrange(pheno, prop) %>%
  as.data.frame()

#wilcox test for visualizing significance
z.mean_comp_tbl_calc <- z.prop.global_abs.diffs %>%
  group_by(pheno, prop) %>%
  pairwise_wilcox_test(abs.diff ~ dataset, comparisons=list(c("cf.lm", "cf.gam"), c("cf.gam", "cf.gamlss"), c("cf.lm", "cf.gamlss")),
                       p.adjust.method = "fdr") 
```

```{r}
z.mean_comp_tbl <- z.mean_comp_tbl_calc %>%
  mutate(comp = factor(paste(group2, group1, sep="_"), ordered=TRUE, levels=c("cf.lm_cf.gam", "cf.lm_cf.gamlss", "cf.gamlss_cf.gam"))) %>%
  arrange(prop, comp) %>%
  add_xy_position(x="prop", fun="max", comparisons=list(c("cf.lm", "cf.gam"), c("cf.gam", "cf.gamlss"), c("cf.lm", "cf.gamlss"))) %>%
  add_significance("p.adj")

#get max w/in each pheno, prop & dataset for placement
z.max_abs.errs <- z.prop.global_abs.diffs %>%
  group_by(pheno, prop, dataset) %>%
  summarize(max_err = max(abs.diff)) %>%
  ungroup() %>%
  pivot_wider(id_cols=c(pheno, prop), names_from=dataset, values_from=max_err, names_prefix="max_")

z.mean_comp_tbl2 <- full_join(z.mean_comp_tbl, z.max_abs.errs)

#just use significance from actual stats tests

stats_z_for_plot <- inner_join(z.mean_comp_tbl2, z.t.test.df_global_filt)
#kinda hacky way of fixing positions
stats_z_for_plot.corrected <- stats_z_for_plot %>%
  mutate(p.adj.signif = ifelse(sig_fdr == "FALSE", "ns", "*"),
         xmax=case_when(group1=="cf.gamlss" | group2== "cf.gamlss" ~ (x+.266667),
                        TRUE ~  x),
         xmin=case_when(group2=="cf.lm" ~ (x-.266667),
                        TRUE ~  x),
         y.position=case_when(comp == "cf.lm_cf.gamlss" ~ max_cf.lm + .16,
                              comp == "cf.lm_cf.gam" ~ max_cf.lm + .1,
                              TRUE ~ max_cf.gam + 0.05))

z.t.test.df_global_filt %>%
  dplyr::select(prop, comp, pheno, sig_fdr) %>%
  dplyr::filter(sig_fdr == FALSE)
```
